The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-12 paper/ms.tex
improved intro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

The exoplanet field is evolving.
At the beginning, Doppler spectroscopy by the Geneva and California groups
led to the first exoplanet detections (CITE: Mayor 95, Butler, Marcy).
Some of these planets transited (CITE: Henry, Charbonneau).
Despite the geometric rarity of transits, photometric monitoring can
be performed in parallel; with precise spectroscopy this has not
yet been achieved.
Parallel photometric monitoring enabled thousands of planet detections
with the Kepler spacecraft (CITE: Borucki, Morton).
The abundance of planets from Kepler taught us about statistics
(CITE: Howard, Fressin, Petigura).
By nature of its design, Kepler left open two major avenues for
improvement: (i) brighter stars, (ii) rare weirdos.
TESS (CITE: Ricker), by nature of its small, wide-field cameras, and
nearly all-sky coverage, can capitalize on both.

One class of rare weirdo to which TESS is sensitive is stars in
clusters.  For brevity, we use the term ``cluster'' to refer to open
clusters, moving groups, associations, and star-forming regions.
Each of the $\sim$1000 star clusters of the Milky Way is a gift to
astrophysics, providing a sample of stars that vary widely in mass
but all have approximately the same age and composition.

Cluster stars have been photometered from the ground for a while
(CITE: Joel thesis, Cambridge group).
A few clusters, NAME1 and NAME2, were observed by Kepler in its prime
mission (CITE: Meibom).
And a few more, most notably X,Y, and Z, were observed in K2's
ecliptic mission (CITE).

TESS holds the promise to deliver the most homogeneous and
comprehensive cluster photometric survey in history.  Based on the
cluster membership database of \citet{Kharchenko_et_al_2013} and the
TESS apparent magnitude calculator of \citet{Jaffe_Barclay_2017}, we
estimate that $10^5$ cluster members brighter than $T=16$ will be
observed in the northern ecliptic hemisphere's full-frame images.

However, there are formidable obstacles to deriving precise photometry
from the {\it TESS} images because of the relatively poor angular
resolution.  Almost all of the clusters are within 10 degrees of the
Galactic plane (see Figure~1), where the problems with crowding and
complex backgrounds are so severe that the {\it TESS}\, Science Team
has neglected that portion of the sky in their planet simulations
\citep{Sullivan_et_al_2015}. Similarly, the {\it TESS}\, Candidate
Target List deprioritizes all objects within $15^\circ$ of the
galactic plane~\citep{stassun_TIC_2018}, which includes 90\% of all
star clusters.  The large pixel size and the high stellar surface
density will make aperture photometry unreliable.  Yet, aperture
photometry is the basis of the official {\it TESS} data reduction
pipeline and almost all reduction methods that have been applied to
{\it Kepler} and {\it K2} data.

We have begun to produce photometry from the TESS images.
For the time being, we are adopting the difference imaging (or
optionally, ``image subtraction'') technique, because of its
benefits in modelling complex backgrouds in crowded regions.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The exoplanet field is evolving.
% At the beginning, Doppler spectroscopy by the Geneva and California groups
% led to the first exoplanet detections (CITE: Mayor 95, Butler, Marcy).
% Some of these planets transited (CITE: Henry, Charbonneau).
% Despite the geometric rarity of transits, photometric monitoring can
% be performed in parallel; with precise spectroscopy this has not
% yet been achieved.
% Parallel photometric monitoring enabled thousands of planet detections
% with the Kepler spacecraft (CITE: Borucki, Morton).
% The abundance of planets from Kepler taught us about statistics
% (CITE: Howard, Fressin, Petigura).
% By nature of its design, Kepler left open two major avenues for
% improvement: (i) brighter stars, (ii) rare weirdos.
% TESS (CITE: Ricker), by nature of its small, wide-field cameras, and
% nearly all-sky coverage, can capitalize on both.

% One class of rare weirdo to which TESS is sensitive is stars in
% clusters.  For brevity, we use the term ``cluster'' to refer to open
% clusters, moving groups, associations, and star-forming regions.
% Each of the $\sim$1000 star clusters of the Milky Way is a gift to
% astrophysics, providing a sample of stars that vary widely in mass
% but all have approximately the same age and composition.

\section{Introduction}
\label{sec:intro}

Many evolutionary processes are expected to occur over the lives of
stars and exoplanets; it would be interesting to statistically observe
these changes as functions of time.
However, since dwarf stars do not appreciably change in size or luminosity
until evolving off the main sequence, creative approaches must be used to
infer ages \citep{soderblom_ages_2010}.
In the study of exoplanets, one approach beginning to bear fruit
is to search for planets in open clusters and moving groups.
The ages of these stellar ensembles are inferred through isochrone
analysis, and are typically most constrained by the location of the
main-sequence turnoff and/or the red giant branch (CITE IF TRUE).
Once calibrated, gyrochronology can also be used to verify
the age of a stellar ensemble \citep[{\it
e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
The ages of planets discovered around these cluster stars are then
assumed to equal those of the star.

The first planet detections in open clusters
came from radial velocity measurements of evolved stars in the Hyades
\citep{Sato_et_al_2007}, and in NGC~2423 \citep{lovis_mayor_2007}.
Subsequent spectroscopic searches in Praesepe led to the detection of the first
hot Jupiters in a cluster \citep{Quinn_et_al_2012}, and also the first
multi-planet system \citep{Malavota_et_al_2016}.
There were also additional detections reported in the Taurus
star-forming region (CITE V830 Tau b; Donati et al. 2016, and Cl Tau
b; Johns-Krull et al. 2016, Flagg et al. 2019).
An additional radial velocity survey was conducted by Brucalassi et al
(2017, CITE), following 88 stars in M~67 over 7 years.  They
reported the detections of three hot Jupiters around main sequence
stars, and one giant planet around an evolved star.

The transit method was slow to catch up, despite deep searches of the
M~37 open cluster by \citet{hartman_MMT_IV_2009}, as well as
multi-year searches of nine young clusters in the solar neighborhood
by the Monitor project
\citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
While these studies led to interesting measurements of stellar
rotation \citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as
the discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
\citep{irwin_monitor_PMSEB_2007}, no planet in open clusters were
uncovered.  Transit searches in globular clusters were similarly met
with null results \citep{gilliland_lack_2000,
weldrake_searching_2006}.

Kepler \citep{borucki_kepler_2010} was the first machine to observe a
sufficient number of stars for long enough and with sufficient
precision to detect transiting planets in open clusters:  Kepler-66b
and 67b, in the gigayear-old NGC6811 \citep{Meibom_et_al_2013}.
Though a broken reaction wheel ended the prime Kepler mission, the
repurposed K2 mission \citep{howell_k2_2014} switched between
fields along the ecliptic every quarter-year, and was able to observe
far more clusters and young stars.
In particular, K2's detections through its surveys of the Pleiades,
Hyades, Praesepe, and Upper Sco were a major inspiration for the
present work.

K2-25b, discovered in the Hyades, had a radius ($3.43\,R_\oplus$) that
was larger than older Kepler planets at similar insolation levels
\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
the planet is contracting, or losing its atmosphere (e.g., CITE).
The super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in
Upper Sco, showed that at least some close-in planets must form within
about 10 Myr, excluding long-timescale migration as an explanation for
its origin \citep{Mann_K2_33b_2016,David_et_al_2017}.
Further discoveries included six transiting planets in Praesepe (CITE
Obermeier, Mann 2016 or 2017), a long-period candidate super-Earth in
the Hyades (CITE Vanderburg 2017), K2-136b in the Hyades (CITE
Ciardi+2018, Livingston+2018), the transiting multi-planet system
K2-264bc in Praesepe (CITE Rizzuto+2018, Livingston+2019), as well as
a Jupiter-sized planet orbiting every 24 days around V1298 Tau (CITE
David+2019).
A final related detection was that of three small planets transiting
K2-233 (CITE David 2018).  Though the star was not in a cluster, its
age was determined to be $360_{-140}^{+490}\,{\rm Myr}$ based on
rotation, activity, and kinematic indicators.

Clearly, a significant amount of effort has been and continues to be
devoted towards the discovery and characterization of planets around
young stars.
It would be nice to begin occurrence rate testing, with a machinery
similar to that described by Rizzuto 2017 (CITE).
However, due to the geometric rarity of transits, many tens of
thousands of stars with known ages must be monitored at high precision
for such studies to be statistically robust.

The TESS mission \citep{ricker_transiting_2015} holds the promise to
deliver the most homogeneous and comprehensive cluster photometric
survey in history.  Based on the cluster membership database of
\citet{Kharchenko_et_al_2013} and the TESS apparent magnitude
calculator of \citet{Jaffe_Barclay_2017}, we estimated that $\approx
2\times10^5$ cluster members brighter than $T=16$ will be observed in
the full-frame images over the first two years of TESS observations.
The actual number may be even larger, as cluster membership catalogs
are by no means complete, even at these relatively bright magnitudes
(CITE recent Gaia discoveries of nearby OCs).

We have begun to produce time-series photometry from the TESS images
for stars in ``clusters''~--~a collective term we adopt for open
clusters, moving groups, stellar associations, and star-forming
regions.
We are also including some stars that we suspect are young due to
combined photometric and astrometric indicators (see
\S~\ref{sec:starselection}).
Our eventual hope is to discover giant transiting planets, and probe
the exoplanet size and separation distributions for planets younger
than 1 Gyr.

%FIXME: this paragraph needs improvement.
Unfortunately, there are formidable obstacles to deriving precise
photometry from the {\it TESS} images because of the relatively poor
angular resolution.  Almost all of the clusters are within 10 degrees
of the Galactic plane (see FIGURE~1), where the problems with crowding
and complex backgrounds are so severe that the {\it TESS}\, Science
Team has neglected that portion of the sky in their planet simulations
\citep{Sullivan_et_al_2015}. Similarly, the {\it TESS}\, Candidate
Target List deprioritizes all objects close to the galactic
plane~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which includes 90\%
of all star clusters.  The large pixel size and the high stellar
surface density will make aperture photometry unreliable.  Yet,
aperture photometry is the basis of the official {\it TESS} data
reduction pipeline and almost all reduction methods that have been
applied to {\it Kepler} and {\it K2} data.
We have therefore adopted the difference imaging technique (also
dubbed ``image subtraction''), because of its benefits in modelling
complex backgrouds in crowded regions.
